\begin{thebibliography}{9}

\bibitem{gwo} 
Mirjalili, S., Mirjalili, S.M. and Lewis, A., 2014. Grey wolf optimizer. Advances in engineering software, 69, pp.46-61.
 
\bibitem{mogwo} 
Mirjalili, S., Saremi, S., Mirjalili, S.M. and Coelho, L.D.S., 2016. Multi-objective grey wolf optimizer: a novel algorithm for multi-criterion optimization. Expert Systems with Applications, 47, pp.106-119.
 
\bibitem{gwo-review} 
Faris, H., Aljarah, I., Al-Betar, M.A. and Mirjalili, S., 2017. Grey wolf optimizer: a review of recent variants and applications. Neural Computing and Applications, pp.1-23.

\bibitem{mgwo-1}
Mittal N, Singh U, Sohi BS (2016) Modified grey wolf optimizer
for global engineering optimization. Appl Comput Intell Soft
Comput 2016:8

\bibitem{mgwo-2}
Koza JR (1992) Genetic programming: on the programming of
computers by means of natural selection. MIT Press, Cambridge

\bibitem{mgwo-3}
Dudani AR, Chudasama K (2016) Partial discharge detection in
transformer using adaptive grey wolf optimizer based acoustic
emission technique. Cogent Eng 3(1):1256083

\bibitem{mgwo-4}
Kishor A, Singh, PK (2016) Empirical study of grey wolf
optimizer. In: Proceedings of fifth international conference on
soft computing for problem solving. Springer, pp 1037–1049

\bibitem{mgwo-5}
Saremi S, Mirjalili SZ, Mirjalili SM (2015) Evolutionary population
dynamics and grey wolf optimizer. Neural Comput Appl
26(5):1257–1263

\bibitem{mgwo-6}
Zhang S, Zhou Y (2015) Grey wolf optimizer based on Powell
local optimization method for clustering analysis. Discret Dyn
Nat Soc 2015:17

\bibitem{mgwo-7}
Luo Q, Zhang S, Li Z, Zhou Y (2015) A novel complex-valued
encoding grey wolf optimization algorithm. Algorithms 9(1):4

\bibitem{mgwo-8}
Yang B, Zhang X, Yu T, Shu H, Fang Z (2016) Grouped grey
wolf optimizer for maximum power point tracking of doubly-fed
induction generator based wind turbine. Energy Convers Manag
133:427–443

\bibitem{mgwo-9}
Kamboj VK (2016) A novel hybrid pso-gwo approach for unit
commitment problem. Neural Comput Appl 27(6):1643–1655

\bibitem{mgwo-10-1}
Jitkongchuen D (2015) A hybrid differential evolution with grey
wolf optimizer for continuous global optimization. In: 2015 7th
international conference on information technology and electrical
engineering (ICITEE). IEEE, pp 51–54

\bibitem{mgwo-10-2}
Zhu A, Xu C, Li Z, Wu J, Liu Z (2015) Hybridizing grey wolf
optimization with differential evolution for global optimization
and test scheduling for 3d stacked soc. J Syst Eng Electron
26(2):317–328

\bibitem{mgwo-11}
Pan TS, Dao TK, Chu SC, et al (2015) A communication
strategy for paralleling grey wolf optimizer. In: International
conference on genetic and evolutionary computing. Springer,
pp 253–262

\bibitem{mogwo-1}
Tsai PW, Dao TK, et al (2016) Robot path planning optimization
based on multiobjective grey wolf optimizer. In: International
conference on genetic and evolutionary computing.
Springer, pp 166–173

\bibitem{mogwo-2}
Lu C, Xiao S, Li X, Gao L (2016) An effective multi-objective
discrete grey wolf optimizer for a real-world scheduling problem
in welding production. Adv Eng Softw 99:161–176

\bibitem{mogwo-3}
Hai Phong Private Universty (2016) Estimation localization in
wireless sensor network based on multi-objective grey wolf
optimizer. In: Advances in information and communication
technology: proceedings of the international conference, ICTA
2016, vol 538. Springer, p 228

\bibitem{mopso}
Coello, C.A.C., Pulido, G.T. and Lechuga, M.S., 2004. Handling multiple objectives with particle swarm optimization. IEEE Transactions on evolutionary computation, 8(3), pp.256-279.

\end{thebibliography}

